Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Remove inaccurate sentence

These systems, however, allow publication of data sufficient to verify tallies. Relying on
cryptography to ensure secrecy, each system involves exposure of cryptographically-hidden vote
counts that can be used to ensure that -- given all votes cast -- the final tallies are correct.

>>>>

These systems, however, allow publication of data sufficient to verify tallies while relying on
cryptography to ensure secrecy.
